Data Analysis and Modeling

### 2018-05-30 papers/full_paper.Rmd
Fix host models

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')

  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')

  source(file.path(code_path, 'functions', 'abb_Functions.R'))

@@

```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}

  load(file.path(data_path, 'analyzed', 'analyzed_data.RData'))

@@

 ##  Create the variable section of table
 full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
 names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

@@

  # Print
  print(x.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,17,22,22),
       caption.placement='top')

@@

 pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c))
 names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

@@

 # Print
 print(px.full,
       include.rownames=FALSE,
       hline.after=c(-1, 0, 17, 22, 22),
       caption.placement='top')

@@

```{r build_blockfreq, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

  str.col <- col_df$rgb[1]

  ## Create table of host block frequencies

  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') +
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

```{r build_blockrate, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

 ## Create scatter of block rate vs block periods

  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * extr_par)) +
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') +
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

```{r plot_hostblock, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostblock}Host Blocking Tendencies'}

  ggMultiPlots(host.block.freq, block.rate.period, cols=2)

@@

```{r build_hostbase, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

  # Create a background plot for the host location plots

  base.host <- ggplot(str_tdf,
                    aes(x=block_rate, y=blockpertime)) +
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') +
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%',
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4],
                #                            abb.col[7], abb.col[9])) +
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))

```{r build_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

  ## Create individual host location plots

  ps.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  mu.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
               size=.4)  +
    ggtitle('Multi-Platform User')

  un.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

```{r plot_hosttypes, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.cap='\\label{hostcat}Host Categories'}

  ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)

```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}

 ## Build plot

  host.type.bar <- ggplot(str_tdf, aes(host_type, fill=host_type)) +
    geom_bar() +
    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
                               col_df$rgb[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') +
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
    #ggtitle('short-term Host Types') +
    theme(plot.title = element_text(hjust = 0.5))

 ## Plot

  host.type.bar

@@

 hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), h1$table.coef,
                                    h2$table.coef, h3$table.coef))
 names(hfull.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
 hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel', 'Strict Cancel')

@@

 print(xh.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,17,22,22),
       caption.placement='top')

>>>>

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')
  setwd('..')
  source(file.path(getwd(), 'functions', 'abb_Functions.R'))

@@

```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, results='hide'}

  setwd('..')
  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

@@

 ##  Create the variable section of table
 full.table <- as.data.frame(cbind(rep('x', length(m1c)), m1c, m2c, m3c))
 names(full.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 full.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel')

@@

  # Print
  print(x.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,16,21,21),
       caption.placement='top')

@@

 pfull.table <- as.data.frame(cbind(rep('x', length(pm1c)), pm1c, pm2c, pm3c))
 names(pfull.table) <- c('Variable', 'Model 1', "Model 2", "Model 3")
 pfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel')

@@

 # Print
 print(px.full,
       include.rownames=FALSE,
       hline.after=c(-1, 0, 16, 21, 21),
       caption.placement='top')

@@

![Host Blocking Tendencies](C:/Code/research/airbnbMelbourne/images/block_rate.png)

@@

![Host Categories](C:/Code/research/airbnbMelbourne/images/host_scat.png)

![Host Category Counts](C:/Code/research/airbnbMelbourne/images/host_bar.png)

@@

 hfull.table <- as.data.frame(cbind(rep('x', nrow(h1)), h1$table.coef,
                                    h2$table.coef, h3$table.coef))
 names(hfull.table) <- c('Variable', 'Profit-Seekers', "Multi-Platform", "Unknown")
 hfull.table$Variable <- c('Intercept', 'House (Type)', '2 Bed & 1 Bath',
                          '2 Bed & 2 Bath', '3 Bed & 1 Bath', '3 Bed & 2 Bath',
                          '3 Bed & 3 Bath','4 Bed & 2 Bath','4 Bed & 3 Bath', 
                          'City (Submarket)',
                          'Suburban (Submarket)', 'Rural (Submarket)',
                          'Beach (Submarket)', 'Guests per Bedroom',
                          'Minimum Stay', 'Flexible Cancel')

@@

 print(xh.full,
       include.rownames=FALSE,
       hline.after=c(-1,0,16,21,21),
       caption.placement='top')

### 2018-05-30 scripts/3_data_prep.Rmd
Fix host models

>>>>

Next, a small number of properties have very long minimum stays, we round any minimum stay greater than 7 days to be 7 days.

  str_tdf <- str_tdf %>%
   dplyr::mutate(min_stay = if_else(min_stay > 7L, 7L, min_stay))

  str_tdf <- str_tdf %>%
   dplyr::mutate(guest_per_bed = round(max_guests / bedrooms, 2)) %>%
   dplyr::mutate(guest_per_bed = if_else(guest_per_bed > 4, 4, guest_per_bed))

### 2018-05-30 scripts/4_data_analysis.Rmd
Fix host models

  str_col = col_df$rgb[1]

@@

  load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))

@@

  glm_lik_host <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + as.factor(canc_policy),
                      family=binomial(link='logit'),
                      data=str_tdf)

  glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + as.factor(canc_policy),
                      family=binomial(link='logit'),
                      data=str_tdf)

@@

  lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                          I(max_guests/bedrooms) + min_stay + as.factor(canc_policy))

  pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                          I(max_guests/bedrooms) + min_stay + as.factor(canc_policy))

>>>>

@@

  load(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData'))
  str_col = col_df$rgb[1]

@@

  glm_lik_host <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        guest_per_bed + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)

  glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)

@@

  lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))

  pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))
